Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Updated Figure1 label

nldr1 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("a", cex = 1.3)

nldr1c <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a")

@@

nldr5 <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("e", cex = 1.3)

nldr5c <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("e")

>>>>

nldr1 <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("a", c(0.08, 0.9), cex = 1.3)

nldr1c <- umap_pbmc |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.1, size=1, colour='#a65628') +
  interior_annotation("a", c(0.08, 0.9))

@@

nldr5 <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour=clr_choice) +
  interior_annotation("e", c(0.08, 0.9), cex = 1.3)

nldr5c <- tsne_pbmc |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#4daf4a') +
  interior_annotation("e", c(0.08, 0.9))
